\documentclass[a4paper,12pt,titlepage]{article}
%\usepackage[T1]{fontenc}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[portuguese]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{indentfirst}
\usepackage{graphicx}
%\usepackage{times}
\usepackage{ucs}
\usepackage{float}    
\usepackage{fancyvrb}   
\usepackage{verbatim}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{epigraph}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{lipsum}

\hypersetup{
    colorlinks=true,       
    linkcolor=black,          
    citecolor=black,   
    filecolor=black,  
    urlcolor=black  
}

\hyphenation {di-re-cio-na-men-to} 

%\renewcommand*{\familydefault}{\ttdefault}
\lstset{columns=fullflexible,basicstyle=\ttfamily}

\title{\large
Universidade Federal de Minas Gerais \\ \
Computer Science Department \\ \
\\[1cm]
2015/2016 Plan\\ \
\\[1cm]
\textbf{\Large A Characterization of the Brazilian Academic Research from the Perspective of Sub-areas}
\\[1cm]
}

\author{\large Alberto Hideki Ueda \\[0.5cm] 
\\[3cm] }

\date{\textsc{Belo Horizonte\\ \
November 22, 2015}}

\begin{document}
\maketitle

\section{Activities} 

\begin{enumerate}
\item{\textbf {WSDM-Cup}}: submit a new ranking with the 3rd Microsoft Academic Graph now available. Submit a paper with an overview of our methodology and basic strategies.
\item{\textbf {Last courses}}: conclude the two remaining courses: Recommendation Systems and Computer Architecture. Last deadline: December 10.
\item{\textbf {Project: Problem definition}}: clarify the scope of the project. What we want to exploit/answer and what we do not.
\item{\textbf {Dataset}}: define the dataset to be used (Microsoft Graph/Lattes/DBLP) and which part of data is relevant to work. Verify what we already have and which information have to be extracted. 
\item{\textbf {JCDL: Experiments}}: test the hypotheses defined in tasks 3 and 4. Evaluate the results against some of our ground-truths.
\item{\textbf {JCDL}}: submit a paper to JCDL.
\item{\textbf {Master's project proposal}}: submit a project proposal to UFMG/DCC.
\item{\textbf {Teacher assistant}}: complete this program requirement for Master's degree.
\item{\textbf {Project experiments}}: do more and deeper experiments in order to obtain a good characterization of academic research, possibly in another areas as physics, biochemical and economics.
\item{\textbf {Master's dissertation}}: write the dissertation.
\end {enumerate}

{\centering \begin{tabular}{| l | c | c | c | c | c | c | c | c |} \hline
\multicolumn{9}{| c |}{\textbf{\normalsize 2015/2016 Schedule}} \\[2pt] \hline
      Task &  Nov   &  Dec   &  Jan   & 	 Feb  & 	  Mar  &	   Apr  &    May &  Jun 	 \\ \hline
WSDM-Cup  &    X   &    X   &    X   &        &        &        &        &        \\ \hline
Last courses &    X   &    X   &        &        &        &        &        &        \\ \hline
Project: Problem definition &        &    X   &        &        &        &        &        &        \\ \hline
Dataset &        &    X   &    X   &        &        &        &        &        \\ \hline
JCDL: Experiments &        &    X   &    X   &        &        &        &        &        \\ \hline
JCDL &        &        &    X   &        &        &        &        &        \\ \hline
Master's project proposal &        &        &        &    X   &        &        &        &        \\ \hline
Teacher assistant &        &        &        &        &   X    &    X   &    X   &    X   \\ \hline
Project experiments &        &        &        &    X   &   X    &    X   &    X   &        \\ \hline
Master's dissertation &        &        &        &        &        &    X   &    X   &    X   \\ \hline
\end{tabular}}

%\footnotesize
{
\centering 
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{2}{| c |}{\textbf{\normalsize Important Dates}} \\[2pt] \hline
      
\multicolumn{2}{| c |}{JCDL} \\[2pt] \hline
         Paper submission deadline & January 17, 2016        \\ \hline
         Notification of acceptance &	 March 16, 2016     \\ \hline
         Final camera-ready deadline &	 April 6, 2016      \\ \hline
 
\multicolumn{2}{| c |}{WSDM-Cup} \\[2pt] \hline
         Phase 2 submissions & December 1, 2015	       \\ \hline
         Phase 2 evaluation closes & January 31, 2016 	\\ \hline
         WSDM Cup Workshop     & February 22, 2016	    \\ \hline
\end{tabular}
}

\section{Research Questions} 

\begin{enumerate}
\item Given a sub-area and one simple venue as reference, could we naturally construct a reliable network of relevance? How the result changes if we increase the number of venues?
\item How we can effectively compare the academic production around the world? Is it a good idea to adopt a sub-area perspective?
\item How significant is the scientific impact of brazilian research groups if we compare it to the impact of other research groups (e.g. in US and Europe)?
\end{enumerate}

\end{document}


