%I would like to thank ….
%I would like to express my gratitude to ....
%I acknowledge the contribution of ....

I would like to express my gratitude to several people for their support over the course of my master's degree. 
%
First of all, I am specially grateful to Berthier for, in a few words, giving me all support in my life-changing decision of come back to the academia. I always felt he believed in me but I never could understand why. However, his trustfulness and guidance were vital to bring me here. 
%
I am also thankful to Nivio, for giving me a key to LATIN at my first day at UFMG. His pieces of advice, self-motivation, and full commitment to work will always remain with me.
%
I would also like to thank Sabir~Ribas very warmly, for being a reference of a good graduate student for me, a focused person, and, most of all, a dear friend.

A great deal of gratitude is due to all professors who also guided or deeply inspired me somehow: Edmundo, Rodrygo, Wagner Meira, Newton, Jussara, Omar, Vinicius dos Santos, and José Coelho.
%
I am also extremely grateful to all my peers at LATIN, who taught me what a good research lab is. In particular, Bruno Laporais, for motivating me by simply staying at the lab, Marlon Dias, for our great partnership and his inspirational quest for excellence, Jordan, Felipe, and Rafael.

To my wife Camila, my Wonder Woman, my role model, and my greatest friend, for making this dream possible. Her incommensurable support at every single moment of this journey was more than I could ever have asked for. No words of mine can describe how I am grateful to her. 

I must also thank my friends Victor Melo, Rensso Mora, Carlos Caetano, Evelin Amorim, and Sonia Borges, for all their support. 
%To Felipe Guo and his fantastic memoir ``Ph.D. Grind''. 
And heartfelt thanks to Chris Cornell, whose songs and great voice I listened so much while writing this dissertation. 
%To my inexplicable good fortune. 

The next and last paragraph is only in Portuguese because there is no sense of writing in another language. 

\textit{
Para meus pais, Akira e Yumiko, que deram a mim e à minha irmã uma formação muito além das expectativas de todos, apesar de tantas dificuldades. Obrigado também pelos valores transmitidos que, como tudo que vale realmente a pena, não podemos comprar ou vender.
} 

% Sinto-me sortudo por ter crescido nesta família, dentre tantos bilhões de possibilidades. outras, bilhões sistemas estelares e galáxias.

